Linear regression for approximating real and synthetic data

### 2022-10-10 doc/paper.tex
More paper

\lstinputlisting[language=Python, firstline=53, lastline=64]{../src/utils.py}

@@

The correctness of our linear regression can be confirmed by running our debug function (the so called SkrankeFunction)\footnote{this can be done by running \texttt{\$ python3 task\_b.py --debug -n 2 --noscale}}, which is a second degree polynomial where $b_0 = 0, \; b_1 = 1, \; b_2 = 2$ and so on. The SkrankeFunction (taken from \texttt{src/utils.py}) looks like this

>>>>

\lstinputlisting[language=Python, firstline=56, lastline=64]{../src/utils.py}

@@

The correctness of our Ordinary Least Squares regression can be confirmed by running our debug function (the so called SkrankeFunction)\footnote{this can be done by running \texttt{\$ python3 task\_b.py --debug --noscale -n 2}}, which is a second degree polynomial where $b_0 = 0, \; b_1 = 1, \; b_2 = 2$ and so on. The SkrankeFunction (taken from \texttt{src/utils.py}) looks like this

\lstinputlisting[language=Python, firstline=26, lastline=27]{../src/utils.py}

and the result of our regression is correctly given as $\bm{\beta} = (0 \; 1 \; 2 \; 3 \; 4 \; 5\;)^T$.
